Project Review

### 2023-05-05 code/analysis_code/statisticalanalysis.qmd
Discussion

# Create a scatter plot with ggplot for residuals 
ggplot(residuals_df, aes(x = Predictions , y = Residuals)) +
  geom_point() +
  xlab("Predicted values") +
  ylab("Residuals") +
  ggtitle("Residual Plot")

@@

>>>>

# Create a scatter plot with ggplot for residuals 
Res1 = ggplot(residuals_df, aes(x = Predictions , y = Residuals)) +
  geom_point() +
  xlab("Predicted values") +
  ylab("Residuals") +
  ggtitle("Residual Plot")
Res1

#Save Linear Regression Output Table
table10= here("results", "table10.RDS")
saveRDS(final_fit_metrics, file = table10)

#save figure of predictions vs outcome values 
ggsave(filename = here("results","Predictions_vs_OutcomeValues.png"), plot=plot1)

#save figure of residuals 
ggsave(filename = here("results","Residuals_Plot.png"), plot=Res1)

@@

### Evaluate the final fit for the Lasso model

```{r}
final_fit2 <- 
  final_lasso_wf %>%
  last_fit(data_split)

final_fit_metrics2 <- final_fit2 %>%
  collect_metrics()
final_fit_metrics2

#creating a tibble for predicted values of model
predictions2 = final_fit2  %>%
  collect_predictions

#plotting model predictions vs actual outcome 
plot2 = final_fit2 %>%
  collect_predictions  %>%
    ggplot(aes(x = .pred, y = TOTAL_RATE_DIFF)) +
  geom_smooth(method = "lm", se = FALSE) +
  xlab("Predicted Probability") +
  ylab("Actual Class") +
  ggtitle("Predicted Values vs Actual Outcome Values")
plot2

#plotting the residuals 
residuals2 = predictions$TOTAL_RATE_DIFF - predictions$.pred

#creating a residual data frame 
residuals_df2 = data.frame(TOTAL_RATE_DIFF = predictions$TOTAL_RATE_DIFF, Predictions = predictions$.pred, Residuals = residuals)

# Create a scatter plot with ggplot for residuals 
Res2 = ggplot(residuals_df2, aes(x = Predictions , y = Residuals)) +
  geom_point() +
  xlab("Predicted Values") +
  ylab("Residuals") +
  ggtitle("Residual Plot")

#Save Linear Regression Output Table
table11= here("results", "table11.RDS")
saveRDS(final_fit_metrics2, file = table11)

#save figure of predictions vs outcome values 
ggsave(filename = here("results","Predictions_vs_OutcomeValues.png"), plot=plot2)

#save figure of residuals 
ggsave(filename = here("results","Residuals_Plot.png"), plot=Res2)
```

## Fitting for random forest model

```{r}
rf_mod =
  rand_forest(mtry = tune(), min_n = tune(), trees = 1000) %>% 
  set_engine("ranger") %>% 
  set_mode("regression")
```

## Creating a recipe

```{r}
recipe2 <- recipe(TOTAL_RATE_DIFF ~ ., data = train_data)
```

```{r}
rf_workflow =
  workflow() %>%
  add_model(rf_mod)  %>%
  add_recipe(recipe2)
```

```{r}
rf_res <- 
  rf_workflow %>% 
  tune_grid(CV_fold)
```

```{r}
rf_res %>% show_best("rmse")

best_rf = rf_res %>%
  select_best("rmse")
best_rf
```

### Finalizing random forest model

```{r}
final_rf_wf <- 
  rf_workflow %>% 
  finalize_workflow(best_rf)

final_rf_wf
```

### Evaluate the final fit for the random forest model

```{r}
final_fit3 <- 
  final_rf_wf %>%
  last_fit(data_split)

final_fit_metrics3 <- final_fit3 %>%
  collect_metrics()
final_fit_metrics3

#creating a tibble for predicted values of model
predictions3 = final_fit3  %>%
  collect_predictions

#plotting model predictions vs actual outcome 
plot3 = final_fit3 %>%
  collect_predictions  %>%
    ggplot(aes(x = .pred, y = TOTAL_RATE_DIFF)) +
  geom_smooth(method = "lm", se = FALSE) +
  xlab("Predicted Probability") +
  ylab("Actual Class") +
  ggtitle("Predicted Values vs Actual Outcome Values")
plot3

#plotting the residuals 
residuals3 = predictions$TOTAL_RATE_DIFF - predictions$.pred

#creating a residual data frame 
residuals_df3 = data.frame(TOTAL_RATE_DIFF = predictions$TOTAL_RATE_DIFF, Predictions = predictions$.pred, Residuals = residuals)

# Create a scatter plot with ggplot for residuals 
Res3 = ggplot(residuals_df3, aes(x = Predictions , y = Residuals)) +
  geom_point() +
  xlab("Predicted Values") +
  ylab("Residuals") +
  ggtitle("Residual Plot")

#Save Linear Regression Output Table
table12 = here("results", "table12.RDS")
saveRDS(final_fit_metrics3, file = table12)

#save figure of predictions vs outcome values 
ggsave(filename = here("results","Predictions_vs_OutcomeValues.png"), plot=plot3)

#save figure of residuals 
ggsave(filename = here("results","Residuals_Plot.png"), plot=Res3)
```

### 2023-05-05 products/Manuscript.qmd
Discussion

# Summary
This study aims to conduct a secondary analysis of residents of the black community in Albany, GA that have received at least one dose of the COVID-19 vaccine from September 2022 through February 2023 and live in the one of the three zip codes 31701, 31705 and 31707. The outcome of interest is the difference in vaccination rates by month from September through February. The predictor of interest is the presence of a COVID-19 Vaccine Hesitancy Program Intervention.

{{< pagebreak >}}

@@

## General Background
Back in March 2020, COVID-19 greatly impacted the citizens of the Albany, GA. Early on in the COVID-19 pandemic Albany, GA was ranked the "forth-worst" city hit by COVID-19 in the United States [@grahamrapierHowSmallGeorgia2020]. According to U.S Census Bureau, 74.5% of the total population of the City of Albany is made up by residents that are black. In a study that examined the health outcomes of residents who tested positive for COVID-19 in Albany, GA it was found that 83.3% of 710 patients that were hospitalized for COVID-19 were black[@]. Although there was no differences in hospital mortality found between residents that were black compared to residents that were not black but there was a much higher percentage of hospitalizations due to COVID-19 for residents who were black.

In July 2022, Albany was awarded a 3.9 million dollar grant from the Health and Human Services and the Office of Minority Health in an effort to fund COVID-19 vaccine hesitancy and health literacy programs[]. The Economic Evaluation Research Group (EERG) out of the University of Georgia College of Public Health Department of Health Policy and Management led by Dr. Janani Rajbhandari-Thapa is currently conducting an evaluation on the federally funded programs.

@@

The data is downloaded from the Georgia Department of Public Health Distribution Dashboard ([citation for dashboard pasted here](https://experience.arcgis.com/experience/3d8eea39f5c1443db1743a4cb8948a9c)) which is a publicly available dashboard that displays the current vaccination administered and the up-to-date count of Georgia residents that have been vaccinated.

The data of interest from this dashboard is the data containing the count of residents with at least one dose of the COVID-19 vaccine by census tract by demographics. You can download the data from [the census tract demographic data](https://www.arcgis.com/home/item.html?id=17a8a4af79e5453a9132aaa29fb4ad22) and a description of the data by census tract demographic can be found on the separate dashboard found [here](https://insights.arcgis.com/#/view/08d2c1f995524053b1f9669dd0b0b995).

@@

## Vaccination Trends of the Black Community for Each Zip Code

The was no noticiable increase of vaccination rate for

```{r}
knitr::include_graphics("../results/plot_31701_total_black_vax_rate.png")
```

```{r}
knitr::include_graphics("../results/31705_total_black_vax.png")
```

```{r}
knitr::include_graphics("../results/31707_total_black_vax.png")
```

```{r}
knitr::include_graphics("../results/30815_total_black_vax.png")
```

```{r}
knitr::include_graphics("../results/30907_total_black_vax.png")
```

## Vaccination Trends of the Black Community for Each Zip Code by Gender
```{r}
knitr::include_graphics("../results/31701_Gender_black_vax.png")
```

```{r}
knitr::include_graphics("../results/31705_Gender_black_vax.png")
```

```{r}
knitr::include_graphics("../results/31707_Gender_black_vax.png")
```

```{r}
knitr::include_graphics("../results/30815_Gender_black_vax.png")
```

```{r}
knitr::include_graphics("../results/30907_Gender_black_vax.png")
```

## Vaccination Trends of the Black Community for Each Zip Code by Gender
```{r}
knitr::include_graphics("../results/31701_Age_black_vax.png")
```

```{r}
knitr::include_graphics("../results/31705_Age_black_vax.png")
```

```{r}
knitr::include_graphics("../results/31707_Age_black_vax.png")
```

```{r}
knitr::include_graphics("../results/30815_Age_black_vax.png")
```

```{r}
knitr::include_graphics("../results/30907_Age_black_vax.png")
```

## LASSO Results Visual 
```{r}
knitr::include_graphics("../results/lasso_grid_plot.png")
```

## Final LASSO Results Variable Importance 
```{r}
knitr::include_graphics("../results/final_lasso_plot.png")
```

# References

# Discussion

>>>>

# Summary

This study aims to conduct a secondary analysis of residents of the black community in Albany, GA that have received at least one dose of the COVID-19 vaccine from September 2022 through February 2023 and live in the one of the three zip codes 31701, 31705 and 31707. The outcome of interest is the difference in vaccination rates by month from September through February. The predictor of interest is the presence of a COVID-19 Vaccine Hesitancy Program Intervention.

@@

## General Background

Back in March 2020, COVID-19 greatly impacted the citizens of the Albany, GA. Early on in the COVID-19 pandemic Albany, GA was ranked the "forth-worst" city hit by COVID-19 in the United States [@grahamrapierHowSmallGeorgia2020]. According to U.S Census Bureau, 74.5% of the total population of the City of Albany is made up by residents that are black. In a study that examined the health outcomes of residents who tested positive for COVID-19 in Albany, GA it was found that 83.3% of 710 patients that were hospitalized for COVID-19 were black[@grahamrapierHowSmallGeorgia2020]. Although there was no differences in hospital mortality found between residents that were black compared to residents that were not black but there was a much higher percentage of hospitalizations due to COVID-19 for residents who were black.

In July 2022, Albany was awarded a 3.9 million dollar grant from the Health and Human Services and the Office of Minority Health in an effort to fund COVID-19 vaccine hesitancy and health literacy programs[@thealbanyheraldCityAlbanyReceives]. The Economic Evaluation Research Group (EERG) out of the University of Georgia College of Public Health Department of Health Policy and Management led by Dr. Janani Rajbhandari-Thapa is currently conducting an evaluation on the federally funded programs.

@@

The data is downloaded from the Georgia Department of Public Health Distribution Dashboard (@georgiadepartmentofpublichealthGADPHVaccine) which is a publicly available dashboard that displays the current vaccination administered and the up-to-date count of Georgia residents that have been vaccinated.

The data of interest from this dashboard is the data containing the count of residents with at least one dose of the COVID-19 vaccine by census tract by demographics. You can download the data from the Georgia Department of Public Health Distribution Dashboard and a description of the data by census tract demographic can be found on the
COVID-19 Vaccinations Among Georgia Residents with At Least One Dose By Census Tract Dashboard (@georgiadepartmentofpublichealthCOVID19VaccinationsGeorgia).

@@

## Descriptive Analysis: Vaccination Trends of the Black Community for Each Zip Code

### Zip code 31701
The vaccination rate of the the Black population slightly decreased from a rate of 61% to 60.6% (@fig-1). The vaccination rate for female black residents slightly decreased from 65% to 64% while the male black resident population's vaccination rate increased slightly at 53% to 57%. It is important to note the difference between the vaccination rates of female and male black residents, which is around .1 from September to February (@fig-2). When the black population was stratified by age, the rates were the highest for the ages of 65 and older at 89%. Black residents aged 45-64 had a steady rate of 70%, black residents aged 18-44 had a steady rate of 65%, blacked residents aged 10-17 had a steady rate of 40% and black residents aged 5-9 had a steady rate of 12% (@fig-3).

```{r}
#| label: fig-1
#| fig-cap: "Vaccination Rates for Black Population in the 31701 Zipcode"
knitr::include_graphics("../results/31701_total_black_vax_rate.png")
```

```{r}
#| label: fig-2
#| fig-cap: "Vaccination Rates for Black Population by Gender in the 31701 Zipcode"
knitr::include_graphics("../results/31701_Gender_black_vax.png")
```

```{r}
#| label: fig-3
#| fig-cap: "Vaccination Rates for Black Population by Age in the 31701 Zipcode"
knitr::include_graphics("../results/31701_Age_black_vax.png")
```

### Zip code 31705

The vaccination rate of stayed stable around 48% for the black population in the 31705 zip code (@fig-4). The vaccination rate of female black residents dropped from 51.1% to 49.7% from September to December, but remained stable close to 50% until February. For male black residents the vaccination rate hovered around 44% (@fig-5). After stratifying by age the vaccination rates for the 65+, 44-64, 18-44, 10-17 and 5-9 ages groups were as follows: 85%, 68%, 43%, 35% and 12% (@fig-6).

```{r}
#| label: fig-4
#| fig-cap: "Vaccination Rates for Black Population in the 31705 Zipcode"
knitr::include_graphics("../results/31705_total_black_vax_rate.png")
```

```{r}
#| label: fig-5
#| fig-cap: "Vaccination Rates for Black Population by Gender in the 31705 Zipcode"
knitr::include_graphics("../results/31705_Gender_black_vax.png")
```

```{r}
#| label: fig-6
#| fig-cap: "Vaccination Rates for Black Population by Age in the 31705 Zipcode"
knitr::include_graphics("../results/31705_Age_black_vax.png")
```

### Zip code 31707

The total vaccination rate of black residents in the 31707 zip code was around 50% from September through February (@fig-7). The vaccination rates for the female and male black population were found to be steady around 54% and 44% (@fig-8). The vaccination rates by the age groups 65+, 44-64, 18-44, 10-17 and 5-9 where found to be 98%, 85%, 52%, 37%, and 17% (@fig-9).

```{r}
#| label: fig-7
#| fig-cap: "Vaccination Rates for Black Population in the 31707 Zipcode"
knitr::include_graphics("../results/31707_total_black_vax_rate.png")
```

```{r}
#| label: fig-8
#| fig-cap: "Vaccination Rates for Black Population by Gender in the 31707 Zipcode"
knitr::include_graphics("../results/31707_Gender_black_vax.png")
```

```{r}
#| label: fig-9
#| fig-cap: "Vaccination Rates for Black Population by Age in the 31707 Zipcode"
knitr::include_graphics("../results/31707_Age_black_vax.png")
```

### Zip code 30815

The total vaccination rate for the black population was 44% in the 30815 zip code from September through February (@fig-10). The vaccination rates for black female and male residents were 49% and 38% (@fig-11). The vaccination rates by the age groups 65+, 44-64, 18-44, 10-17 and 5-9 where found to be 78%, 60%, 38%, 31%, and 8% (@fig-12).

```{r}
#| label: fig-10
#| fig-cap: "Vaccination Rates for Black Population in the 30815 Zipcode"
knitr::include_graphics("../results/30815_total_black_vax_rate.png")
```

```{r}
#| label: fig-11
#| fig-cap: "Vaccination Rates for Black Population by Gender in the 30815 Zipcode"
knitr::include_graphics("../results/30815_Gender_black_vax.png")
```

```{r}
#| label: fig-12
#| fig-cap: "Vaccination Rates for Black Population by Age in the 30815 Zipcode"
knitr::include_graphics("../results/30815_Age_black_vax.png")
```

### Zip code 30907

The total vaccination rate for the black population was 54% in September and dropped to around 53% in February in the 30907 zip code (@fig-13). The vaccination rates for black female and male residents were 60% and 45% (@fig-14). The vaccination rates by the age groups 65+, 44-64, 18-44, 10-17 and 5-9 where found to be 95%, 64%, 63%, 33%, and 11% (@fig-15).

```{r}
#| label: fig-13
#| fig-cap: "Vaccination Rates for Black Population in the 30907 Zipcode"
knitr::include_graphics("../results/30907_total_black_vax_rate.png")
```

```{r}
#| label: fig-14
#| fig-cap: "Vaccination Rates for Black Population by Gender in the 30907 Zipcode"
knitr::include_graphics("../results/30907_Gender_black_vax.png")
```

```{r}
#| label: fig-15
#| fig-cap: "Vaccination Rates for Black Population by Age in the 30907 Zipcode"
knitr::include_graphics("../results/30907_Age_black_vax.png")
```

## Statistical Analysis

### Bivariate Analysis Through Simple Linear Regression

#### Demagraphic Vaccination Rates as Predictors
The following bivariate simple linear regression models were performed on each predictor variable of interest and the main outcome of interest which is total vaccination rate difference by month among the black population in each zip code. The following predictors produced results that were found not to be statistically significant predictors at the 0.05 significance level: Total vaccination rate by month among the black population, the male vaccination rate by month among the black population, the female vaccination rate by month among the black population, age ranges of 5-9, 10-17, 18-44, 45-64, 65+ vaccination rate by month among the black population. Of these predictors, based on p-values the best predictor of total vaccination rate difference by month was the vaccination rate for the age range of 45-65 which had a p-value of 0.52 (@tbl-1). The coefficient estimate for the vaccination rate for the age range of 45-65 was 0.004 which indicates for every one-unit increase of vaccination rate for the age range of 45-65 the total vaccination rate difference by month among the black population increased by 0.004 units (@tbl-1).

```{r}
#| label: tbl-1
#| fig-cap: "Simple Linear Regression Output for the Vaccination Rate of the Age Range of 45-64 Among the Black Population as a Predictor"
readRDS(file = here("results", "table7.RDS")) 
```

#### Intervention as a Predictor
The Intervention variable is a binary predictor where "1" indicates a zip code hosting the COVID-19 Health Literacy and Vaccine Hesitancy Program and "0" indicates a zip code that is not hosting a program. When this was fitted in a simple linear regression model with total vaccination rate difference by month among the black population in each zip code as the outcome, the resulting coefficient estimate was 0.068 and a p-value of 0.55 (@tbl-9). The p-value of 0.55 was not significant at the 0.05 level, however, it was among the lowest p-values when compared to the p-values for the demographic vaccination rate predictor variables. In addition, the coefficient estimate of 0.068 is the largest positive coefficient among all other predictors, indicating the total vaccination rate difference by month among the black population increases by 0.068 or 6.8% in zip codes with an intervention program. Although this result is not supported by the p-value when evaluated for significance at the 0.05 level, it is notable to observe an increase in total vaccination rate by month when intervention is the only predictor being controlled for.

```{r}
#| label: tbl-9
#| fig-cap: "Simple Linear Regression Output for Intervention as a Predictor "
readRDS(file = here("results", "table9.RDS")) 
```

## Full Model Fitting and Evalutation

### Tree Model 
After running a Regression Tree Model using all the predictors and the main outcome of total vaccination rate difference by month among the black population in each zip code the best fit model was found to have an RMSE value of 0.37584439 and an R-squared value of 0.06730276 (@tbl-10).

```{r}
#| label: tbl-10 
#| fig-cap: "Best Fit Tree Model Metrics"
readRDS(file = here("results", "table10.RDS")) 
```

### Lasso Model 
The Lasso Regression Model produced a best fit regression model that had an RMSE value of 0.30444322 and a R-squared of 0.09234508 (@tbl-11).

```{r}
#| label: tbl-11
#| fig-cap: "Best Fit LASSO Metrics"
readRDS(file = here("results", "table11.RDS")) 
```

### Random Forrest
The Random Forrest Regression model for the full model produced a best fit model with an RMSE metric of 0.3716112 and an R-squared of 0.2279387 (@tbl-12).

```{r}
#| label: tbl-12
#| fig-cap: "Best Fit Random Forrest Metrics"
readRDS(file = here("results", "table12.RDS")) 
```

# Discussion
Since July of 2022, The Health and Human Services and the Office of Minority Health have funded COVID-19 vaccine hesitancy and health literacy prgrams in Albany, GA that have been in action since October of 2022 [@thealbanyheraldCityAlbanyReceives]. This analysis has produced a data set from the Georgia Department of Public Health COVID-19 vaccination data that contains vaccination rates by demographic and total vaccination rate in zip codes that the COVID-19 vaccine hesitancy and health literacy programs were enrolled compared to a two control zip codes that were matched via SRI and and SVI. The intention of this analysis was to examine whether the zip codes with the COVID-19 vaccination and health literacy intervention had a notable increase of vaccination rates from the months of September 2022 through February 2023.

Descriptive statistics were used to examine the vaccination rates among the zip codes of 31701, 31705 and 31707 by month from September 2022 through February 2023. No notable increase were observed

# Limitations 
# References

### 2023-05-05 reviews/Hatfield Review.qmd
Discussion

### Feedback and Comments
 The background and introduction are  thorough and proide good motiviation to the importance of the study.

The abstract could use help with clarity, perhaps reframe the study some: 
The outcome of interest is the change in the proportion of residents vacccinated over time from September - February. The predictor of interest is the COVID-19 vaccine hesitancy program intervention. It would be helpful also to help contextualize the three zip codes of interest.

@@

The hypotheis and questions can be more explicitly stated in the manuscript. For example, in the objectives section you mention data cleaning methods. The objective should be stated more succintly and explicitly:

@@

Your hypothesis is a little unclear to me too. For example, you are looking for an increase in the number of Albany citizens who receive the vaccine in the time period. However, this is a value that can't decrease. So are you looking for an increase in the trend (interrupted tiem series), and increase in the daily rate among unvaccinated (where your denominator will change daily), an increase in the zip codes of interest versus other zip codes where targeted interventions werent applied? The objective/hypothesis might need to be fleshed out a bit more.

### Summary assessment
* question/hypotheses fully clear

@@

The data structure is well explained and sources described. It is meddled in the with the importation and cleaning. I would rather encourage the author to separate the findings a bit.

### Summary assessment
* source and overall structure of data well explained

@@

Data cleaning process is well described. Similar to comment above, it is interwoven with description of the data sources. The manuscript would benefit from separate paragraphs discussing these elements and some editorial review (e.g., ensuring run-on sentences are shortened, fragments removed). Some mentions of "data were cleaned" without explaining exaclty how. An example would be:

"For this analysis, we decided to exclude purina body condition scores as it was implemented later in the study, and most dogs do not have that information. The remaining columns were cleaned to make the data more consistent and in the format required for statistical analysis. "

could be streamlined to: 
"We excluded condition scores because they were not consistently collected and had high numbers of missing values. We recoded XXXX variables from XXX to XXX to facilitate easier statistical analysis.""

@@

### Summary assessment
* defensible but not optimal analysis

@@

### Summary assessment
* results are presented ok, with room for improvement

@@

* strong, complete and clear discussion

@@

## Structure
Is the project well structured? Are files in well labeled folders? Do files have reasonable names? Are all "junk" files not needed for analysis/reproduction removed? By just looking at files and folders, can you get an idea of how things fit together?

@@

@@

@@

@@

* strong level of thorougness

## Further comments
---

>>>>

### Feedback and Comments
 The background and introduction are  thorough and provide good motiviation to the importance of the study.

The abstract could use help with clarity, perhaps even a reframe the study some: 
The outcome of interest is the change in the proportion of residents vacccinated over time from September - February. The predictor of interest is the COVID-19 vaccine hesitancy program intervention. It would be helpful also to help contextualize the three zip codes of interest.

@@

The hypothesis and questions can be more explicitly stated in the manuscript. For example, in the objectives section you mention data cleaning methods. The objective should be stated more succinctly :

@@

Your hypothesis is a little unclear to me too. For example, you are looking for an increase in the number of Albany citizens who receive the vaccine in the time period. However, this is a value that can't decrease. So are you looking for an increase in the trend (interrupted tiem series), and increase in the daily rate among unvaccinated (where your denominator will change daily), an increase in the zip codes of interest versus other zip codes where targeted interventions weren't applied? The objective/hypothesis might need to be fleshed out a bit more.

### Summary assessment
* question/hypotheses somewhat explained

@@

The data structure is well explained and sources described. However, the author presents the findings as percents but states that the data source provides counts. He does not provide details on where the denominators for calculating percents come from. I see some population data in the processed dataset so I would encourage the author to describe the sources of that data too.

### Summary assessment
* source and overall structure of data somewhat explained

@@

Data processing is explained. However, I would be curious as to some of the data points. For example, the authors describe a decrease in vaccination rates over time. First, I would note that the decreases are small (<1%). Second, it is unclear how the decreases could occur (i.e., once a resident is vaccinated, they can't unvaccinated themself). This could be due to variation in the data or other factors, but should be addressed.

The author also does the analyses over time in separate figures for each zip code. It would be helpful to have these on the same graph, perhaps grouped by color for if they are an intervention zip code or control zip code.

@@

 There is limited analysis description in the manuscript. Per the analysis code file it appears there is detailed analysis with cross-fold validation. However, this is not described in the text.

### Summary assessment
* wrong/inadequate analysis

@@

### Feedback and Comments
The line graphs showing trends over time in the different zip codes are helpful. However, they could be improved with some additioanl work on the visualizations. In the manuscript the results for the advanced analysis are limited and not well described.

### Summary assessment
* results are poorly presented, hard to understand, poor quality

@@

* major parts of discussion missing or wrong

@@

## Structure

### Feedback and Comments
The project is well organized and the quarto files with code are well documented and easy to file. It is unclear to me if processingcode and processingcode2 quarto files need to reamin. I would update the readme section in that folder to make it clear which file does what part you are describing.

@@

### Feedback and Comments
The project is well documented. Some of the rationale for some of the caclulations is missing in some of the analysis files, but it is easy to understand the analytic parts.

@@

### Feedback and Comments
The analysis appears reproducible. However, some parts do appear to typed in (e.g., calculation of some rates) where it may be better to program the calculations to ensure typos don't affect your results.

@@

The analysis seems thorough in the quarto files. However, from the manuscript file it is unclear.

@@

* decent level of thoroughness

## Further comments
This study could use a bit more thought and effort into the analysis and interpretation. I think the quarto files show a lot of really good exploratory analyses. The manuscript could use work to better describe the work and the findings.

I don't think the references are formatted correctly, as they are also not populating in the manuscript. 
---
